---
title: "2018_Data_Recode"
author: "Kevin Vogt-Lowell"
date: "4/9/2021"
output: html_document
---

## Rename 2018 variables to match those in 2016

```{r ch1}
suppressPackageStartupMessages(library(tidyverse))

suppressWarnings(data2018_original <- read_csv("2018_mh_data_original.csv"))

data2018_recode <- data2018_original %>% rename(c(
"self_employed" = "<strong>Are you self-employed?</strong>",

"company_size"	= "How many employees does your company or organization have?",

"tech_company"	= "Is your employer primarily a tech company/organization?",

"has_tech_role_in_company"	= "Is your primary role within your company related to tech/IT?",

"employer_provides_mh_coverage"	="Does your employer provide mental health benefits as part of healthcare coverage?",

"knows_employer_mh_coverage_options" = "Do you know the options for mental health care available under your employer-provided health coverage?",

"employer_has_discussed_mh_formally"="Has your employer ever formally discussed mental health (for example, as part of a wellness campaign or other official communication)?",

"employer_has_mh_resources_and_options" = "Does your employer offer resources to learn more about mental health disorders and options for seeking help?",

"anonymity_guaranteed" = "Is your anonymity protected if you choose to take advantage of mental health or substance abuse treatment resources provided by your employer?",

"difficulty_asking_for_mh_related_medical_leave" = "If a mental health issue prompted you to request a medical leave from work, how easy or difficult would it be to ask for that leave?",

"comfortable_discussing_mh_with_coworkers"="Would you feel comfortable discussing a mental health issue with your coworkers?",

"comfortable_discussing_mh_with_supervisors" =  "Would you feel comfortable discussing a mental health issue with your direct supervisor(s)?",

"has_medical_coverage_mhd_included" = "Do you have medical coverage (private insurance or state-provided) that includes treatment of mental health disorders?",

"knows_local_or_online_mhd_resources"="Do you know local or online resources to seek help for a mental health issue?",

"revealed_mhd_to_clients_or_business_contacts"="<strong>If you have been diagnosed or treated for a mental health disorder, do you ever reveal this to clients or business contacts?</strong>",

"negative_impact_of_revealing_mhd_to_clients_contacts"= "If you have revealed a mental health disorder to a client or business contact, how has this affected you or the relationship?",

"productivity_affected_by_mh"	= "Do you believe your productivity is ever affected by a mental health issue?",

"percentage_of_work_time_affected_by_mh" = "If yes, what percentage of your work time (time performing primary or secondary job functions) is affected by a mental health issue?",

"previous_employers"="<strong>Do you have previous employers?</strong>",

"prev_employer_provided_mh_coverage"="<strong>Have your previous employers provided mental health benefits?</strong>",

"knew_prev_employer_mh_coverage_options" ="<strong>Were you aware of the options for mental health care provided by your previous employers?</strong>",

"prev_employer_discussed_mh_formally"	= "Did your previous employers ever formally discuss mental health (as part of a wellness campaign or other official communication)?",

"prev_employer_had_mh_resources_and_options"	= "Did your previous employers provide resources to learn more about mental health disorders and how to seek help?",

"prev_employer_anonymity_guaranteed" = "Was your anonymity protected if you chose to take advantage of mental health or substance abuse treatment resources with previous employers?",

"comfortable_discussing_mh_with_prev_coworkers"	= "<strong>Would you have been willing to discuss your mental health with your coworkers at previous employers?</strong>",

"comfortable_discussing_mh_with_prev_supervisors"	= "Would you have been willing to discuss your mental health with your direct supervisor(s)?",

"willing_to_bring_up_ph_in_interview_y_n"	= "Would you be willing to bring up a physical health issue with a potential employer in an interview?",

"willing_to_bring_up_ph_in_interview_y_n_reason"	= "Why or why not?",

"willing_to_bring_up_mh_in_interview_y_n"= "Would you bring up your mental health with a potential employer in an interview?",

"willing_to_bring_up_mh_in_interview_y_n_reason" = "Why or why not?_1",

"observed_or_experienced_unsupportiveness_or_bad_response"	= "<strong>Have you observed or experienced an unsupportive or badly handled response to a mental health issue in your current or previous workplace?</strong>",

"observations_of_response_to_mhd_of_others_made_less_likely_to_reveal"= "Have your observations of how another individual who discussed a mental health issue made you less likely to reveal a mental health issue yourself in your current workplace?",

"family_history_of_mhd"	= "Do you have a family history of mental illness?",

"had_mhd_past"	= "Have you had a mental health disorder in the past?",

"has_mhd_now"	= "Do you currently have a mental health disorder?",

"had_mhd_diagnosed_by_professional"	= "Have you ever been diagnosed with a mental health disorder?",

"has_sought_treatment_from_professional"	= "Have you ever sought treatment for a mental health disorder from a mental health professional?",

"mhd_interferes_with_work_when_effectively_treated"	= "If you have a mental health disorder, how often do you feel that it interferes with your work <strong>when being treated effectively?</strong>",

"mhd_interferes_with_work_when_not_effectively_treated"	= "If you have a mental health disorder, how often do you feel that it interferes with your work <strong>when</strong> <em><strong>NOT</strong></em><strong> being treated effectively (i.e., when you are experiencing symptoms)?</strong>",

"age"	= "What is your age?",

"gender"	= "What is your gender?",

"country_of_residence" = "What country do you <strong>live</strong> in?",

"state_of_residence"	= "What US state or territory do you <strong>live</strong> in?",

"country_of_work"	= "What country do you <strong>work</strong> in?",

"state_of_work"	= "What US state or territory do you <strong>work</strong> in?")
)
  
```


## Remove 2018 variables not included in 2016 survey, and rearrange variables to match 2016 demographic/survey split

```{r ch2}

data2018_recode <- data2018_recode %>% transmute(
self_employed,
company_size,
tech_company,
has_tech_role_in_company,
employer_provides_mh_coverage,
knows_employer_mh_coverage_options,
previous_employers,
age,
gender,
country_of_residence,
state_of_residence,
country_of_work,
state_of_work,
family_history_of_mhd,
had_mhd_past,
has_mhd_now,
had_mhd_diagnosed_by_professional,
has_sought_treatment_from_professional,
mhd_interferes_with_work_when_effectively_treated,
mhd_interferes_with_work_when_not_effectively_treated,
employer_has_discussed_mh_formally,
employer_has_mh_resources_and_options,
anonymity_guaranteed,
difficulty_asking_for_mh_related_medical_leave,
comfortable_discussing_mh_with_coworkers,
comfortable_discussing_mh_with_supervisors,
has_medical_coverage_mhd_included,
knows_local_or_online_mhd_resources,
revealed_mhd_to_clients_or_business_contacts,
negative_impact_of_revealing_mhd_to_clients_contacts,
productivity_affected_by_mh,
percentage_of_work_time_affected_by_mh,
prev_employer_provided_mh_coverage,
knew_prev_employer_mh_coverage_options,
prev_employer_discussed_mh_formally,
prev_employer_had_mh_resources_and_options,
prev_employer_anonymity_guaranteed,
comfortable_discussing_mh_with_prev_coworkers,
comfortable_discussing_mh_with_prev_supervisors,
willing_to_bring_up_ph_in_interview_y_n,
willing_to_bring_up_ph_in_interview_y_n_reason,
willing_to_bring_up_mh_in_interview_y_n,
willing_to_bring_up_mh_in_interview_y_n_reason,
observed_or_experienced_unsupportiveness_or_bad_response,
observations_of_response_to_mhd_of_others_made_less_likely_to_reveal)
```

##recode relevant variable values for response consistency across datasets

```{r}
#change the response values in negative_impact_of_revealing_mhd_to_clients_contacts to match those in 2016

data2018_recode$negative_impact_of_revealing_mhd_to_clients_contacts <- recode(data2018_recode$negative_impact_of_revealing_mhd_to_clients_contacts,
                                                                                   "Negatively" = "Yes", 
                                                                                   "Positively" = "No", 
                                                                                   "No change" = "No")

#gender recode

male_list <- c("Cis male" = "M", "cis male" = "M", "Cis Male" = "M", "cis man" = "M","Cis-male" = "M", "cisdude" = "M", "Cisgender male" = "M", "Dude" = "M",
               "I'm a man why didn't you make this a drop down question. You should of asked sex? And I would of answered yes please. Seriously how much text can this take?" = "M", "m" = "M", "M" = "M", "M|" = "M", "mail" = "M", "male" = "M", "Male" = "M", "MALE" = "M",
               "Male (cis)" = "M", "male, born with xy chromosoms" = "M", "Male." = "M", "Malel" = "M", "Malr" = "M", "man" = "M", "Man" = "M",  "mtf" = "M", 
               "Sex is male" = "M"
               )
female_list <- c("*shrug emoji* (F)" = "F", "Cis female" = "F", "Cis woman" = "F", "Cis-Female" = "F", "Cis-woman" = "F", "cisgender female" = "F",
                 "Cisgender Female" = "F", "Cisgendered woman" = "F", "f" = "F", "F" = "F", "fem" = "F", "female" = "F", "Female" = "F", "Female (cisgender)" = "F",
                 "Female (props for making this a freeform field, though)" = "F", "Female assigned at birth" = "F", 
                 "Female or Multi-Gender Femme" = "F", "female-bodied; no feelings about gender" = "F", "female/woman" = "F", "fm" = "F",
                 "I identify as female" = "F", "I identify as female." = "F", "woman" = "F", "Woman" = "F"
                 )
non_binary_list <- c("AFAB" = "GQ","Agender" = "GQ","Androgynous" = "GQ", "Bigender" = "GQ", "Demiguy" = "GQ", "Enby" = "GQ", "Female/gender non-binary." = "GQ",
                "Fluid" = "GQ", "genderfluid" = "GQ", "gender non-conforming woman" = "GQ", "Genderfluid" = "GQ", "Genderfluid (born female)" = "GQ",
                "Genderflux demi-girl" = "GQ", "genderqueer" = "GQ", "Genderqueer" = "GQ", "genderqueer woman" = "GQ", "human" = "GQ",
               "Human" = "GQ", "Male (or female, or both)" = "GQ", "Male (trans, FtM)" = "GQ", "male 9:1 female, roughly" = "GQ", 
               "Male/genderqueer" = "GQ", "N/A" = "GQ", "NB" = "GQ", "nb masculine" = "GQ", "non binary" = "GQ", "non-binary" = "GQ", "Nonbinary" = "GQ",
               "Nonbinary/femme" = "GQ", "none" = "GQ", "none of your business" = "GQ", "Ostensibly Male" = "GQ", "Other" = "GQ", "Other/Transfeminine" = "GQ",
               "Queer" = "GQ", "She/her/they/them" = "GQ", "SWM" = "GQ", "Trans female" = "GQ", "Trans man" = "GQ", "Trans woman" = "GQ", "transgender" = "GQ",
               "Transgender woman" = "GQ", "Transitioned, M2F" = "GQ", "Unicorn" = "GQ")

data2016_recode$gender <- recode(data2016_recode$gender, !!!male_list, !!!female_list, !!!non_binary_list)

data2018_recode$gender <- recode(data2018_recode$gender, !!!male_list, !!!female_list, !!!non_binary_list)

```


##Add year data to both data sets

```{r}

data2016_recode <- data2016_recode %>% 
  mutate("year" = "2016") %>% 
  select(year, everything())

data2018_recode <- data2018_recode %>% 
  mutate("year" = "2018") %>% 
  select(year, everything())

```


## Split 2018 data into demographic and survey groups

```{r ch3}

data2018_demographics <- data2018_recode %>% select(2:21)

data2018_survey <- data2018_recode %>% select(22:46)

```

## Join full, demographic, and survey data based on shared variables

```{r ch4}

#join full recoded 2016 and 2018 datasets
all_common_variables <- intersect(colnames(data2016_recode), colnames(data2018_recode))

combined_data <- rbind(data2016_recode[, all_common_variables], data2018_recode[, all_common_variables])

```

##Join demographic and survey data based on shared variables

``` {r}
#join the demographic and survey datasets separately
common_demographic_variables <- intersect(colnames(data2016_demographics), colnames(data2018_demographics))

combined_demographic_data <- rbind(data2016_demographics[, common_demographic_variables], data2018_demographics[, common_demographic_variables])

common_survey_variables <- intersect(colnames(data2016_survey), colnames(data2018_survey))

combined_survey_data <- rbind(data2016_survey[, common_survey_variables], data2018_survey[, common_survey_variables])

```
