---
title: "Initial Checks"
author: "Nanna Katrin"
date: "18/03/2021"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)

```

## Selecting relevant columns
Select relevant columns that shed light on demographics of the people in the dataset  

```{r divide}
dat <- read_csv("/Users/Nanna/Desktop/MA415/Project/final-project-brains/dataset/mental-heath-in-tech-2016_20161114.csv", col_types = cols())
dat_demographics <- dat %>% select(1:3,17,46:53, 56:63)
names(dat_demographics)

```

## Sex

```{r sex}
#what sexes are in there
dat_demographics %>% group_by(`What is your gender?`) %>% summarise(count = n()) %>% arrange(desc(count)) %>% ungroup()
```

Looks like there are **67** different categorisations of sex in the dataset, a lot of work ahead......Looks like more men than women/other


## Age

```{r age}

dat_demographics %>% group_by(`What is your age?`) %>% summarise(count = n()) %>% arrange(desc(count)) %>% ungroup()



#range
range(dat_demographics$`What is your age?`)

#some less than 18
sum(dat_demographics$`What is your age?`< 18)
dat_demographics %>% filter(`What is your age?`<18) %>% select(`What is your age?`)

#histogram without outliers:
dat_demographics %>% filter(`What is your age?`>=18 & `What is your age?`< 100) %>% ggplot()+geom_histogram(aes(x = `What is your age?`))

#mean age excluding outliers:
dat_demographics %>% filter(`What is your age?`>=18 & `What is your age?`< 100) %>% pull(`What is your age?`) %>% mean(na.rm = TRUE)
```

Some very strange values in age extreme outliers to remove, otherwise a relatively young sample- mean around 30 years



## Geography

```{r geo}

#country
table(dat_demographics$`What country do you live in?`)

#country live vs work:
dat_demographics %>%  group_by(`What country do you live in?`, `What country do you work in?`) %>% summarise(count = n()) %>% ungroup()

#state if US
table(dat_demographics$`What US state or territory do you live in?`)

#remote workers?
count(dat_demographics,`Do you work remotely?`) %>% mutate(prop = n/sum(n))
```


A lot of different countries = **COOL**, most from US/UK: around 70%. Some people not working and living in the same country. Many states. Very spread out in terms of remote work.



## Work conditions

```{r workCond}

##self employed ratio
dat_demographics %>% group_by(`Are you self-employed?`) %>% summarise(count = n()) %>% mutate( prop = count/sum(count)) %>%  ungroup()

##company size
dat_demographics %>% group_by(`How many employees does your company or organization have?`) %>% summarise(count = n()) %>% ungroup()

```

## Mental health problems

```{r mentalh}
library(stringr)

#Different levels of mental health probs:
 dat_demographics %>% group_by(`Have you been diagnosed with a mental health condition by a medical professional?`) %>% summarise(count = n()) %>% mutate(prop = count/sum(count)) %>% ungroup()

dat_demographics %>% group_by(`Do you have a family history of mental illness?`) %>% summarise(count = n()) %>% mutate(prop = count/sum(count)) %>% ungroup()

dat_demographics %>% group_by(`Have you had a mental health disorder in the past?`) %>% summarise(count = n()) %>% mutate(prop = count/sum(count)) %>% ungroup()

dat_demographics %>% group_by(`Do you currently have a mental health disorder?`) %>% summarise(count = n()) %>% mutate(prop = count/sum(count)) %>% ungroup()

#just a quick overview of different conditions
#table(dat_demographics$`If yes, what condition(s) have you been diagnosed with?`)






```


